API design for machine learning software: experiences from the scikit-learn project

### 2013-09-10 paper.tex
Gensim's algos actually don't always take O(1) space
(And when they do, it's commonly the second pass through the data
that does.)
trim FeatureUnion example

\texttt{FeatureUnion} objects combine multiple transformers into a single one
that concatenates their outputs. A union of two transformers that
map input having $d$ features to $d'$ and $d''$ features respectively is
a transformer that maps its $d$ input features to $d' + d''$ features.
This generalizes in the obvious way to more than two transformers.
In terms of API, a \texttt{FeatureUnion} takes as input a list of transformers.
Calling \texttt{fit} on the union is the same as calling \texttt{fit}
independently on each of the transformers and then joining their outputs.

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
Figure~\ref{pca-union} illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.

\begin{figure*}[b]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest

@@

Pipeline([("feat_union", union),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
         ]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
\caption{A union of linear PCA and kernel PCA for feature extraction.}
\label{pca-union}
\end{figure*}

>>>>

\texttt{FeatureUnion} objects combine multiple transformers into a single one
that concatenates their outputs. A union of two transformers that
produce outputs with (resp.) $d_1$ and $d_2$ features, is
a transformer that produces outputs with $d_1 + d_2$ features.
This generalizes in the obvious way to more than two transformers.
Calling \texttt{fit} on the union is the same as calling \texttt{fit}
independently on each of the transformers and then joining their outputs.

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
Figure~\ref{pca-union} illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
and feeds those to an $\ell_2$-regularized logistic regression model.

\begin{figure*}[b]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA

@@

Pipeline([("feat_union", union),
          ("log_reg", LogisticRegression(penalty="l2"))
         ]).fit(X_train, y_train)
\end{pythoncode}
\caption{A union of linear PCA and kernel PCA for feature extraction.}
\label{pca-union}
\end{figure*}
